|

### 2020-10-13 manuscript.Rmd
minor updates in rmd

Which leads to the next point, what is the relation between self-reports and EMG?

@@

From page 10: "Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163). The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumina- tion second (t(29) = 2.513, p = 0.018, d = 0.903). In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first"...

>>>>

@@

"Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163). The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumina- tion second (t(29) = 2.513, p = 0.018, d = 0.903). In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first".
